Music Adaptation: Analysis for selected stimuli

### 2021-09-16 material/expstimuli/audio/analysis/expression/stim_a/ioi_onset.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Articulation")
p_ioi
```

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

>>>>

### Plot
#### Box plot
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
ioi_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, TrialNr)]

p_ioi <- ggplot(data = ioi_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Non-Expression")
p_ioi
```

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr)]
cv
```

#### Box plot
```{r cv_box, echo = FALSE}
cv_trial <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

### 2021-09-16 material/expstimuli/audio/analysis/expression/stim_a/kv.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r kv_bar,  echo = FALSE}
p_kv <- ggplot(data = kv, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Articulation")
p_kv
```

>>>>

### Plot
#### Box plot

```{r kv_bar,  echo = FALSE}
kv_trial <- dt_kv[Subcomponent == "Legato" | Subcomponent == "Staccato", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Subcomponent)]

p_kv <- ggplot(data = kv_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Articulation")
p_kv
```

### 2021-09-16 material/expstimuli/audio/analysis/expression/stim_d/ioi_onset.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Dynamics")
p_ioi
```

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

>>>>

### Plot
#### Box plot
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
ioi_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, TrialNr)]

p_ioi <- ggplot(data = ioi_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Dynamics")
p_ioi
```

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr)]
cv
```

```{r cv_box, echo = FALSE}
cv_trial <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

### 2021-09-16 material/expstimuli/audio/analysis/expression/stim_d/kv.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r kv_bar,  echo = FALSE}
p_kv <- ggplot(data = kv, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Dynamics")
p_kv
```

>>>>

### Plot
#### Box plot

```{r kv_bar,  echo = FALSE}
kv_trial <- dt_kv[Subcomponent == "Forte" | Subcomponent == "Piano", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr, Subcomponent)]

p_kv <- ggplot(data = kv_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  facet_grid(Subcomponent ~ .) +
  labs(y = "Key Velocity", subtitle = "KV: Performing-Dynamics")
p_kv
```

### 2021-09-16 material/expstimuli/audio/analysis/stim_n/ioi_offset.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Non-Expression")
p_ioi
```

@@

```{r outlier, echo = FALSE}
ioi_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, TrialNr)]

excluded_ioi <- ioi_trial[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r nrow(ioi_trial)-nrow(excluded_ioi)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

>>>>

### Plot
#### Box plot
- A dashed line represents the ideal tempo

```{r ioi_bar,  echo = FALSE}
ioi_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr, TrialNr)]

p_ioi <- ggplot(data = ioi_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Non-Expression")
p_ioi
```

@@

```{r outlier, echo = FALSE}
excluded_ioi <- ioi_trial[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r nrow(ioi_trial)-nrow(excluded_ioi)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr)]
cv
```

#### Box plot
```{r cv_box, echo = FALSE}
cv_trial <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

### 2021-09-16 material/expstimuli/audio/analysis/stim_n/ioi_onset.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'IOI-Offset Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

Description: This is a rough overview of non-expressive performance (IOI-Offset) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

@@

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

# Valid performances (exclude outliers)
- Exclude mean IOIs outside 3SD

@@

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

## 2. All - group
- Average CV

@@

# Valid performances (exclude outliers)
- Exclude mean CVs outside 3SD

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./offset_valid.csv")
```

>>>>

---
title: 'IOI-Onset Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

Description: This is a rough overview of non-expressive performance (IOI-Onset) from [music-teaching (experiment2)](https://github.com/atsukotominaga/music-teaching/tree/main/experiment-2).

@@

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

@@

# Valid performances (exclude IOIs outliers)
- Exclude mean IOIs outside 3SD

@@

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
## 2. All - group
- Average CV

@@

# Valid performances (exclude CVs outliers)
- Exclude mean CVs outside 3SD

@@

```{r export, include = FALSE}
fwrite(excluded_cv, "./onset_valid.csv")
```

### 2021-09-16 material/expstimuli/audio/tweaked/analysis.Rmd
moved to audio file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# calculate the diff between each KOT mean and grandMean
tweak_data <- dt_kot[grepl("dyn_only", MidFile) | grepl("low", MidFile) & SubArt != "NA", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
tweak_data$Diff <- abs(tweak_data$Mean-kot_grandMean)
tweak_data

@@

## Histogram (Fixed KOT)
```{r kot-distribution-fixed, echo = FALSE}
gghistogram(dt_kot[SubArt != "NA"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# Export stimuli with fixed KOT as mid files
```{r export, include = FALSE}
# fix time for onset and offset data
data_offset$timeFixed <- data_onset$time
data_offset$timeFixed <- data_offset$time
for (midfile in unique(tweak_data$MidFile)){
   # offset[i] = onset[i+1]+KOT[i]
   for (i in 1:nrow(data_onset[MidFile == midfile])-1){
      data_offset[MidFile == midfile][i]$timeFixed <- data_onset[MidFile == midfile][i+1]$time+dt_kot[MidFile == midfile][i]$FixedKOT
   }
}

for (stim in unique(data_onset$MidFile)){
   onset <- data_onset[MidFile == stim]
   offset <- data_offset[MidFile == stim]
   instance <- rbind(onset, offset)
   # round timeFixed
   instance$timeFixed <- round(instance$timeFixed, 0)
   # Note_On/Off >> 1 or 0
   instance$KeyOnOff <- 0
   instance[event == "Note On"]$KeyOnOff <- 1
   # sort by timeFixed
   instance <- instance[order(timeFixed)]

>>>>

# calculate the diff between each KOT mean and grandMean
tweak_data <- dt_kot[grepl("dyn_only", MidFile) | grepl("low", MidFile) & SubArt != "NA", .(N = .N, Mean = mean(KOT), SD = sd(KOT)), by = .(MidFile)]
tweak_data$Diff <- round(abs(tweak_data$Mean-kot_grandMean), 0)
tweak_data

@@

d KOT)
```{r kot-distribution-fixed, echo = FALSE}
gghistogram(dt_kot[SubArt != "NA"], x = "FixedKOT", color = "SubArt", facet.by = "MidFile", bins = 50, rug = TRUE)
```

@@

# Export stimuli with fixed KOT as mid files
```{r export, include = FALSE}
# remove unnecessary columns
data_onset$IOI <- NULL
data_onset$KOT <- NULL
data_onset$Diff <- NULL
# fix time for onset and offset data
data_onset$timeFixed <- data_onset$time
data_offset$timeFixed <- data_offset$time
for (midfile in unique(tweak_data$MidFile)){
   # offset[i] = onset[i+1]+KOT[i]
   for (i in 1:nrow(data_onset[MidFile == midfile])-1){
      data_offset[MidFile == midfile][i]$timeFixed <- data_onset[MidFile == midfile][i+1]$time+dt_kot[MidFile == midfile][i]$FixedKOT
   }
}

# export each instance as txt file
for (stim in unique(data_onset$MidFile)){
   onset <- data_onset[MidFile == stim]
   offset <- data_offset[MidFile == stim]
   instance <- rbind(onset, offset)
   # Note_On/Off >> 1 or 0
   instance$KeyOnOff <- 0
   instance[event == "Note On"]$KeyOnOff <- 1
   # sort by timeFixed
   instance <- instance[order(timeFixed)]
